---
title: "HW 3"
author: "CC"
date: "10/14/2019"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(collapse = TRUE, message = FALSE)
```

## Problem 1

# Load Libraries and Instacart Data
```{r}
library(tidyverse)
library(p8105.datasets)
library(knitr)
data(instacart)
```

# Describe the Dataset
```{r}
instacart %>%
  group_by(aisle) %>%
  summarize(n = n()) %>%
  view()
```
This dataset is quite large, with `r nrow(instacart)` observations from 131,209 unique users. There is a single order per user, and each row represents a product from an order. For example, user 1 has an order id of 2539329, which functions as their unique identifier, and they ordered from instacart on Monday, the second day of the week at 8AM. The 1st item they added to their cart was Soda, listed in the product name column. There are a few other variables of interest, including whether or not the user has ordered an item in the past (reordered) and days since the user last ordered from instacart (days_since_prior_order). In total there are `r ncol(instacart)` variables.

There are 134 aisles, and by far the aisles with the most orders are fresh veggies and fresh fruits, with over 150,000 items ordered in each. This is followed by the packaged veggies/fruits aisle, from which about 78,000 items have been ordered. The next most popular aisles include dairy products like yogurt, packaged cheese, and milk.

# Making a Plot
```{r}
count(instacart, aisle, name = "aisle_count") %>%
  arrange(desc(aisle_count))
  
plot = 
  instacart %>%
  count(aisle, name = "aisle_count") %>%
  filter(aisle_count > 10000) %>%
  ggplot(aes(x = reorder(aisle, -aisle_count), y = aisle_count)) + geom_bar(stat = "identity") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5)) +
  labs(
    title = "Number of Items From Popular Aisles",
    x = "Aisle",
    y = "Number of Items"
  )
  plot
```
This plot is organized with the aisles on the axis, and their labels have been flipped to be perpendicular to the axis in order to increase legibility. The plot has also been ordered in a descending fashion, with the aisles from which the greatest number of items have been ordered on the left side, and the aisles with the least items ordered on the right side. This plot shows a clear right skew.

# Making a Table: Most Popular Items in Aisles
```{r}
instacart %>%
  group_by(product_name, aisle) %>%
  summarize(
    n_ordered = n()) %>%
  group_by(aisle) %>%
  filter(aisle %in% c("baking ingredients", "dog food care", "packaged vegetables fruits"),
         min_rank(desc(n_ordered)) < 4 ) %>%
  arrange(n_ordered, aisle)
```
This table shows the most popular items ordered from the "dog food care", "baking ingredients", and "packaged vegetables fruits" aisles. The aisles are ordered by increasing number of items ordered.

# Making a Table: Mean Hour of The Day Items Are Ordered
```{r}
fun_food = 
  instacart %>%
  rename(order_hour = order_hour_of_day) %>%
  filter(product_name %in% c("Pink Lady Apples", "Coffee Ice Cream")) %>%
  group_by(product_name, order_dow) %>%
  summarize(mean_hour_of_day = mean(order_hour)) %>%
  mutate(
    day_of_week = recode(order_dow,
                         '0' = "Sunday",
                         '1' = "Monday",
                         '2' = "Tuesday",
                         '3' = "Wednesday",
                         '4' = "Thursday",
                         '5' = "Friday",
                         '6' = "Saturday")) %>%
  separate(mean_hour_of_day, into = c("hour", "minutes"), sep = 2) %>%
  mutate(minutes = as.numeric(minutes),
         minutes = round(minutes*60, digits = 0),
         mean_hour_of_day = paste(hour, minutes, sep = ":")) %>%
  select(product_name, day_of_week, mean_hour_of_day) %>%
  pivot_wider(
    names_from = "product_name",
    values_from = "mean_hour_of_day") %>%
  kable(format = "pandoc", caption = "Mean Hour of Day Items Are Ordered")
fun_food
```
This table shows the mean hour each day of the week that two different items, Coffee Ice Cream and Pink Lady Apples, are ordered. Item order times seem to be fairly consistent across the week, meaning that Coffee Ice Cream is often ordered within 3 hours, from 12-15, and Pink Lay Apples are often ordered between 3 hours, from 11-14.

## Problem 2

# Cleaning and Load BRFSS Data
```{r}
data(brfss_smart2010)

brfss = 
brfss_smart2010 %>%
  janitor::clean_names() %>%
  rename(
    state = locationabbr,
    county = locationdesc,
    cll = confidence_limit_low,
    clh = confidence_limit_high) %>%
  select(-data_value_footnote, -data_value_footnote_symbol, -location_id) %>%
  filter(topic == "Overall Health") %>%
  mutate(response = factor(response, c("Poor", "Fair", "Good", "Very good", "Excellent")))
```

# State Observations Across Years
```{r}
brfss_1 = 
  brfss %>%
  filter(year == "2010") %>%
  distinct(state, county) %>%
  count(state) %>%
  filter(n >= 7) %>%
  rename(number_sites = n)
brfss_1


brfss_2 =
  brfss %>%
  filter(year == "2002") %>%
  distinct(state, county) %>%
  count(state) %>%
  filter(n >= 7) %>%
  rename(number_sites = n)
brfss_2
  
```
There were 14 states observed in 2010 at 7 or more locations and 6 states observed in 2002 at 7 or more locations.

# Construct a Dataset and Make a Plot
```{r}
brfss_excellent =  
brfss %>%
  janitor::clean_names() %>%
  filter(response == "Excellent") %>%
  group_by(year, state) %>%
  summarize(data_value_ave = mean(data_value)) %>%
  ggplot(aes(x = year, y = data_value_ave, group = state, color = state)) + geom_line()
brfss_excellent
```
This plot shows the average value of Excellent responses among state across time from 2002 to 2010.

# Make a Two-Panel Plot
```{r}
data_value_2010 = 
  brfss %>%
  filter(state == "NY", year %in% c("2010", "2006")) %>%
  select(year, response, data_value) %>%
  ggplot(aes(x = response, y = data_value)) + 
  geom_boxplot() +
  facet_grid(~year) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5)) +
  labs(
    title = "Distribution of Responses by Location in New York"
  )
data_value_2010
```
These two histogram plots show the distribution of responses by location solely in the state of New York, between 2006 and 2010. It would appear that overall distributions for each response type increased in 2010.

## Problem 3

# Cleaning Data and Creating Activity Table
```{r}
accel = 
  read_csv("accel_data.csv") %>%
  janitor::clean_names() %>%
  pivot_longer(
    activity_1:activity_1440,
    names_to = "activity_number",
    values_to = "activity") %>%
  separate(activity_number, into = c("activity_name", "minute")) %>%
  mutate(
    day_type = if_else(day %in% c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday"), "day", day),
    day_type = if_else(day_type %in% c("Saturday", "Sunday"), "weekend", day_type),
    minute = as.numeric(minute)) %>%
  select(-activity_name) %>%
  rename(
    day_number = day_id,
    day_name = day
  )
accel
```
The resulting dataset has 6 variables with 50400 observations. It now has a variable defining each activity by number. There is a variable for the week and day of the study each activity took place as an integer value, as well as a variable that says what specific day of the week each activity took place, whether that was a weekday or weekend. Finally we have an integer minute variable for how the minute in the day that an activity took place for.

# Aggregating Data Across Minutes
```{r}
accel_sum = 
  accel %>%
  group_by(day_number) %>%
  summarize(sum_of_day = sum(activity))
kable(accel_sum, format = "pandoc", caption = "Total Activity Per Day")
accel_sum
```
This table has aggregated activity time across minutes, or the total activity time per day. Some general trends seem to be increased activity around the time of weekends, from Friday-Sunday, and decreased overall activity during week days.

# Making a Single Panel Plot: 24hr Activity Each Day
```{r}
plot = accel %>% 
  arrange(minute) %>%
  ggplot(aes(x = minute, y = activity)) +
  geom_point(aes(color = day_name), alpha = 0.75) +
  ylab("Activity") +
  labs(color = "Day of the Week") +
  ggtitle("Daily Activity Levels") +
  scale_x_continuous(
    name = "Time of Day",
    breaks = c(1, 60, 120, 180, 240, 300, 360, 420, 480, 540, 600, 660, 720, 780, 840, 900, 960, 1020, 1080, 1140, 1200, 1260, 1320, 1380, 1440),
    labels = c("12am", "1am", "2am", "3am", "4am", "5am", "6am", "7am", "8am", "9am", "10am", "11am", "12pm", "1pm", "2pm", "3pm", "4pm", "5pm", "6pm", "7pm", "8pm", "9pm", "10pm", "11pm", "12am")) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 0.5))
plot
```
This plot displays the individual's daily activity level by day of the week, and it would appear that he exhibits greater activity levels from Friday-Sunday, as suggested by the previous table. For someone who is experiencing congestive heart failure, it is probably good to maintain as high of a level of activity as possible, while remaining within safe limits for the body. Based on this data, we may suggest that this individual try to improve his activity level during the week, as it may prove beneficial to his cardiovascular health.
